Variance reduction for Markov chains via martingale representations

### 2020-04-24 aap/Revision/vr-mcmc-revision-new-new.tex
update

\begin{lem} Let $\mu(x) = \mu_{0}(x) + \Delta(x)$, where $\mu_0^{\prime}(x) <-m$ for some $m > 0$, $\mu_0(x) \in Lip(L)$ and suppose that $\Delta(x)$ is bounded. Then

>>>>

\begin{lem} Let $(X_p)_{p \geq 0}$ be the ULA-generated Markov chain of the form
X_{p+1} = X_p + \gamma \mu(X_p) + \sqrt{\gamma}\xi_{p+1}, \xi_{p+1} \sim \mathcal{N}(0,1)
 with $\mu(x) = \mu_{0}(x) + \Delta(x)$, where $\mu_0^{\prime}(x) <-m$ for some $m > 0$, $\mu_0(x) \in Lip(L)$ and suppose that $\exists M > 0, \left|\Delta(x)\right| < M$. Then for any Lipschitz function $f$,
